### 2020-07-11 nb/analysis_in_R.Rmd
correct de bruyne goal data

```{r}
LeagueResults <- function(league){

@@

```{r}
results[[2]]
```

```{r}
results[[3]]
```

```{r}
[order(league_table[,1])]
```

```{r}
table
```

```{r}
v <- LeagueResults(events)
```

```{r}
hs <- v[[2]]
```

```{r}
league <- events
```

```{r}
teams <- sort(unique(league$team))

league_table <- matrix(0, nrow=20, ncol=8)
rownames(league_table) <- teams
colnames(league_table) <- c('POS','PTS','W','D','L','GF','GA','GD')
```

```{r}
for (m in unique(league$matchId)){

```{r}
league_table
```

@@

```{r}
league_table['Arsenal',]
```

```{r}
for (match in unique(events$matchId)){

    goals <- 0

```{r}
mId <- unique(events$matchId)[1]
```

```{r}
m <- events[events$matchId==mId,]
```

```{r}
home_goals <- m[m$to_team=='Home Goal',]
```

```{r}
away_goals <- m[m$to_team=='Away Goal',]
```

```{r}
home_goals <- matrix(0, nrow=20, ncol=20)
```

```{r}
away_goals <- matrix(0, nrow=20, ncol=20)
```

```{r}
colnames(home_goals) <- teams
```

```{r}
rownames(home_goals) <- teams
```

```{r}
home
```

```{r}
home_goals
```

```{r}
teams <- sort(unique(events$team))
```

>>>>

```{r}
LeagueResults <- function(league){
    #' Calculate results and table for given national league.

@@

@@

### 2020-07-11 nb/preprocessing.Rmd
correct de bruyne goal data

```{python}

```

```{python}
national_league='England'

```

>>>>

```{python}
# Correct data for De Bruyne's goal vs Chelsea (not an inaccurate pass!)

england_events = pd.read_csv('../data/processed/England.csv')

england_events.at[102730,'eventName'] = 'Shot'
england_events.at[102730,'subEventName'] = 'Goal'
england_events.at[102730,'accurate'] = 1
england_events.at[102730,'to_team'] = 'Away Goal'
england_events.at[102730,'target'] = 'Goal'
england_events.at[102730,'target_y'] = 50

england_events.to_csv('../data/processed/England.csv',index=False)
```
